Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
commit

```{r regression variable specifications}
total_subset %>%
  mutate(ln_income = log(income))
reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))

>>>>

```{r regression variable specifications}
total_subset %>%
  mutate(ln_income = log(income),
         literate = literacy-1,
         female = sex-1,
         no_assist = assist-1,
         not_registered = register-1)
reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))
